Classical Planning with Simulators: \\ Results on the Atari Video Games

### 2015-04-30 ijcai15-paper/paper.tex
Changes updated. need to cut down to 6 pages

Last, in the lookahead, \IW(1) and \BFS\ select an action every $5$ frames, while \UCT\  selects 
an action in every frame.  This means that in order to explore a branch 
$300$ frames deep, UCT gets to choose $300$ actions, while \IW($1$) and \BFS\ 
get to choose $60$ actions, both however using the same $300$ frames from the
budget. For this, we  followed the setup  of \BRFS\ in BNVB 
that also selects actions every $5$ frames, matching the behavior
of the emulator that requests an action also every $5$ frames. Since the 
lookahead budget is given by a maximum number of (new) frames, and the time 
is mostly taken by calls to the emulator, this may not be the best choice  
for $\IW(1)$ and \BFS\ that may therefore not be exploiting all the 
options afforded by the budget. Interestingly, when \UCT\ is limited to one
action each $5$ frames, its performance is reduced by up to a $50$\% in
games where it performs very well (\CrazyClimber), and does not a difference in those games where it does very poorly (\Freeway). We'll look at this further in the future.

>>>>

Last, in the lookahead, \IW(1) and \BFS\ select an action every $5$ frames, while \UCT\  selects 
an action every frame.  This means that in order to explore a branch 
$300$ frames deep, UCT gets to choose $300$ actions, while \IW($1$) and \BFS\ 
get to choose $60$ actions, both however using the same $300$ frames from the
budget. For this, we  followed the setup  of \BRFS\ in BNVB 
that also selects actions every $5$ frames, matching the behavior
of the emulator that requests an action also every $5$ frames. Since the 
lookahead budget is given by a maximum number of (new) frames, and the time 
is mostly taken by calls to the emulator, this may not be the best choice  
for $\IW(1)$ and \BFS\ that may therefore not be exploiting all the 
options afforded by the budget. Interestingly, when \UCT\ is limited to one
action every $5$ frames, its performance is reduced by up to a $50$\% in
games where it performs very well (\CrazyClimber), and does not improve in those games where it performs very poorly (\Freeway).
